A Recipe for Scavenging - the natural history of a behaviour

### 2016-04-28 natural history of scavenging.tex
Fixed weird merge conflict

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Summary_figure/Summary_figure.pdf}
\caption{Factors influencing the proportion of scavenging in a vertebrates' diet. Blue lines indicate a reduction in the factor and red lines indicate an increase.}
%TG: Probably needs some more explanations...
\label{Summary_figure}
\end{figure}

%KH: need paragraph for how do we know something is (was) a scavenger
\section*{Encounter Rate}
All foraging processes depend on the encounter rate between consumer and resource. 
Locomotory speed, foraging time and detection radius all determine the encounter rate between a scavenger and the carcasses it is searching for. 
Alternatively, a species can reduce its metabolic requirements so that it can survive long periods between meals. 
We would thus expect selection pressures to act on the various traits that govern these parameters.

However, as we noted above, encounter rate is also determined by the productivity of the environment, something which the selective forces acting on the scavenging have no control over.

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{timeline_figure/timeLine.pdf}
\caption{The diversity of scavengers through time across air, land and sea. Each species has either direct evidence for it being a scavenger or would be positioned high up on our scavenging scale. The ticks on the x axis represent the transitions for the Palaeozoic-Mesozoic (252.17 Mya) and Mesozoic-Cenozoic (66Mya) boundaries}
\label{Timeline}
\end{figure}

>>>>

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Summary_figure/Summary_figure.pdf}
\caption{Factors influencing the proportion of scavenging in a vertebrates' diet. The black and white gradient bar on the top represent the proportion of scavenging in the diet, ranging from low (- -) on the left hand side to high (+ +) on the right hand side. Blue lines indicate that a reduction in the factor will lead to more or less proportion of scavenging in the diet and red lines indicate an increase.}
%Silhouettes from left to right on each line: \textit{Somelizard ofsomesort}, \textit{Felis silvestris}, \textit{Somelizard ofsomesort}, Diomedeidae, \textit{Antennarius striatus}, \textit{Gyps}, Actinopterigii skeleton, \textit{Stegosaurus} skeleton, \textit{Gyps}, \textit{Crocuta crocuta}, \textit{Rousettus aegyptiacus}, \textit{Crocuta crocuta}.
\label{Summary_figure}
\end{figure}

%KH: need paragraph for how do we know something is (was) a scavenger
\section*{Encounter Rate}
All foraging processes depend on the encounter rate between consumer and resource. 
Locomotory speed, foraging time and detection radius all determine the encounter rate between a scavenger and the carcasses it is searching for and we would thus 
expect selection pressures to act on the various traits that govern these parameters.
Alternatively, selection might drive a species to reduce its metabolic requirements so that it can survive long periods between meals, or expand a species ability to 
process tissues or decaying flesh that might ordinarily be discarded.  However, as we noted above, 
encounter rate is also determined by the productivity of the environment, and ultimately the rate at which carcasses are produced, 
an aspect which the selective forces acting on the scavenger have no influence.

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{timeline_figure/timeLine.pdf}
\caption{The diversity of scavengers through time. Each species has either direct evidence for it being a scavenger or would be positioned high up on our scavenging scale. The three lines represent the three different environments (from top to bottom: aerial, terrestrial and aquatic). Time is represented on the horizontal axis with each third representing respectively the Paleozoic (541 to 252 Mya), the Mesozoic (252 to 66 Mya) and the Cenozoic (66 Mya to the present).}
%Silhouettes from left to right in each different environment: Aerial: \textit{Some pterosaur}, Azhdarchid (which one?), Diomedeidae, \textit{Gyps}, \textit{Some preybird}; Terrestrial: \textit{Some mammaliaform?}, \textit{Some temnospondyl?}, \textit{Allosaurus}?, \textit{Dilophosaurus}?, \textit{Canis lupus?}, \textit{Crocuta crocuta}, \textit{Some shneakyshnake}, \textit{Homo sapiens}; Aquatic: \textit{Tiktaalik}, \textit{Some antiarchplacoderm}, Ichtyosauridae, \textit{Some metriorhynchidae?}, Mosasauridae, \textit{Basilosaurus}, \textit{Carcharodon carcharias}, \textit{Orcinus orca}.
\label{Timeline}
\end{figure}
